Learning and comparing functional connectomes between populations

### 2012-12-29 paper.tex
Iter on intro

\sloppy % Fed up with messed-up line breaks
\section{Introduction}

@@

BOLD signal during rest is typically just 5-10\% lower than during task-based
experiments (cite Raichle,  Mintun, Annu. Rev. Neurosci. 29, 449–476 (2006).)

>>>>

\sloppy % Fed up with messed-up line breaks

\section{Introduction}

Brain functional connectivity captures the synchronization of distant
neural systems via correlations in brain activity. Given that brain
function emerges from the interaction of specialized units, functional
connectivity is an essential part of the description of brain function,
complementary to the localizationist picture emerging from the systematic
mapping of regions recruited in tasks. However, while activation mapping
has a well-defined standard analysis framework that enables
statistically-controlled comparisons across subjects \cite{friston1995},
group-level analysis of functional connectivity is still offers many
challenges.

\cite{kelly2012}

@@

BOLD signal during rest is typically just 5-10\% lower than during task-based
experiments \cite{raichle2006}.
